SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-23 maintex.tex
Updated language for the mass ratio equation

The mass ratio here is defined as, 
\begin{equation}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We emphasize that the MaNGA target is not always the more massive component of the pair. We will define the more massive galaxy of a pair the primary companion and the less massive one the secondary companion.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair survey, and \citet{Thorp:2019} ({\it Blue}), a post-merger survey.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The mass ratio here is defined as, 
\begin{equation}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. In the sample, the MaNGA target is not always the more massive component of the pair. We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
